Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2025-03-10 main.tex
temp

%\AB{Need to add results on the default cluster!}
%
%    \paragraph{Memory-constrained cluster}
The makespan in case of no recomputation becomes invalid as soon as at least one task finds itself in an invalid memory size
situation -- that is, if the scheduler assumed the task's memory to be smaller than actually needed and
assigned the task to a processor with not enough memory capacity.
Due to an extremely constrained memory in this cluster, only 134 experiments out of 1160 
for all algorithm variants end with a valid makespan without recomputation.
In case of \heft, $14$ valid initial makespans were computed.
Out of them, $13$ remain valid until the end, after all the update requests.
The same $13$ experiments end with a valid makespan in case of no recomputation.
So, these workflows require so few resources that there is no point in re-scheduling them.
%$13$ experiments ended with a valid makespan after recomputation in case of \heft, which corresponds to $4.4\%$ success
%rate. However, there were only $14$ successful \heft experiments overall in this setup, so for the successful experiments
%only, the success rate of not recomputing is $92\%$.
In case of \heftmm, all $290$ workflows can be scheduled initially and all the schedules remain valid until the end.
$16$ experiments end with a successful schedule without recomputation, a rate of~$5.5\%$.
\heftblc produces $142$ valid initial schedules and keeps $141$ of them valid until the end.
$50$ experiments are successful without recomputation, a rate of $35\%$ out of all successful final schedules.
\heftbl keeps $105$ schedules valid until the end out of $110$ initial valid schedules.
$55$ remain valid until the end even without recomputation, roughly $50\%$ of all successes.

\heftbl and \heftblc are successful on smaller workflows and fail on larger ones, 
the success of the strategy without recomputation is limited to even the smallest of these smaller workflows.
Thus, the strategy without recomputation delivers valid makespans (independently of the algorithm) 
on $56$ original workflows with $<100$ tasks, $47$ $200$-task ones, $25$ $1000$-task ones, and $6$ $2000$-task ones.

Figure~\ref{fig:updates-ms} shows the increase in makespan in case of no recomputation for these experiments.
With growing size of the workflow, the excess makespan of not recomputing grows -- from $13.9\%$ to $20\%$ for \heftbl,
from $12.7\%$ to $18.7\%$ on \heftblc (but there is no data for the $2000$-task workflows in this case),
% TODO: why not? SK: no (or not enough) valid solutions
$12.1\%$ to $23.5\%$ for \heftmm.
The larger variations for \heft can be explained by the small amount of data -- for instance, there are
only $2$ $200$-task workflows for this case.

\begin{figure}[tb]
    \centering
    \includegraphics[width=0.95\columnwidth] {images/UpdatesMss2}
    \caption{Relative (excess) makespan of \heftbl, \heftblc and \heftmm \new{in case of no recomputation}. Smaller is better.}
    \label{fig:updates-ms}
%    \vspace{-0.3cm}
\end{figure}

>>>>

%\AB{Need to add results on the default cluster!}
%
%    \paragraph{Memory-constrained cluster}
The makespan in case of no recomputation becomes invalid as soon as at least one task finds itself in an invalid memory size
situation -- that is, if the scheduler assumed the task's memory to be smaller than actually needed and
assigned the task to a processor with not enough memory capacity.
Due to an extremely constrained memory in this cluster, only 134 experiments out of 1160 
for all algorithm variants \new{obtain a valid makespan when no recomputation is done}.

In the case of \heft, $14$ valid initial makespans were computed.
Out of them, $13$ remain valid until the end, after all the update requests,
\new{i.e., when accounting for the final execution time of each task and their memory requirement.}
The same $13$ experiments end with a valid makespan in case of no recomputation.
So, these workflows require so few resources that there is \new{nothing to be gained by re-scheduling them.}
%$13$ experiments ended with a valid makespan after recomputation in case of \heft, which corresponds to $4.4\%$ success
%rate. However, there were only $14$ successful \heft experiments overall in this setup, so for the successful experiments
%only, the success rate of not recomputing is $92\%$.

In case of \heftmm, all $290$ workflows can be scheduled initially and all the schedules remain valid until the end,
\new{when new schedules are computed in a dynamic way. Only}  
$16$ experiments end with a successful schedule without recomputation, a rate of~$5.5\%$.

\heftblc produces $142$ valid initial schedules and keeps $141$ of them valid until the end.
$50$ experiments are successful without recomputation, a rate of $35\%$ out of all successful final schedules.

\heftbl keeps $105$ schedules valid until the end out of $110$ initial valid schedules.
$55$ remain valid until the end even without recomputation, roughly $50\%$ of all successes.

\heftbl and \heftblc are successful on smaller workflows and fail on larger ones. 
\new{Note that the success of the strategy without recomputation is limited to  the smallest  workflows,
while a dynamic approach is mandatory when dealing with larger workflows.}
Thus, the strategy without recomputation delivers valid makespans (independently of the algorithm) 
on $56$ original workflows with $<100$ tasks, \new{$47$ workflows with  $200$ tasks, 
$25$ workflows with $1000$ tasks, and only $6$ workflows with $2000$ tasks.
The most representative case for the dynamic experiments is hence \heftmm, since it succeeds
to achieve valid schedules in all cases thanks to recomputation, while most schedules
cannot be successful when no recomputation is done. 
}

Figure~\ref{fig:updates-ms} shows the increase in makespan in case of no recomputation for these experiments.
With growing size of the workflow, the excess makespan of not recomputing grows -- from $13.9\%$ to $20\%$ for \heftbl,
from $12.7\%$ to $18.7\%$ on \heftblc (but there is no data for the $2000$-task workflows in this case),
% TODO: why not? SK: no (or not enough) valid solutions
$12.1\%$ to $23.5\%$ for \heftmm.
The larger variations for \heft can be explained by the small amount of data -- for instance, there are
only \new{two workflows with  $200$ tasks in this case.}

\begin{figure}[tb]
    \centering
    \includegraphics[width=0.95\columnwidth] {images/UpdatesMss2}
    \caption{Relative (excess) makespan of \heftbl, \heftblc and \heftmm  %\new{ 
    when there is no recomputation. Smaller is better.}
    \label{fig:updates-ms}
%    \vspace{-0.3cm}
\end{figure}
